---
title: "NCBA2 Resistome Power Simulations: Shotgun Metagenomic Data Results"
author: "Enrique Doster and Steven Lakin"
date: "May 23, 2018"
output: 
  html_document: 
    theme: readable
---

```{r setup, include=FALSE, cache=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(metagenomeSeq)
library(data.table)
library(ggplot2)
library(vegan)
library(RCurl)
library(kableExtra)
set.seed(154)

## Publicly hosted scripts with helper functions
eval(parse(text=getURL("https://raw.githubusercontent.com/EnriqueDoster/meg_resistome_power_calculation/master/scripts/data_simulation_functions.R", ssl.verifypeer=FALSE)))
eval(parse(text=getURL("https://raw.githubusercontent.com/EnriqueDoster/meg_resistome_power_calculation/master/scripts/meg_utility_functions.R", ssl.verifypeer=FALSE)))

## Data
amr <- newMRexperiment(read.table(text=getURL("https://raw.githubusercontent.com/EnriqueDoster/meg_resistome_power_calculation/master/NCBA2_AMR_analytic_matrix.csv"), header=TRUE, row.names=1, sep=","))

metadata <- read.csv(text=getURL("https://raw.githubusercontent.com/EnriqueDoster/meg_resistome_power_calculation/master/NCBA2_metadata.csv"), header=TRUE)
metadata[, "ID"] <- make.names(metadata[, "ID"])

annotations <- data.table(read.csv(text=getURL("https://raw.githubusercontent.com/EnriqueDoster/meg_resistome_power_calculation/master/megaresbio_annotations_v1.01.csv"), header=TRUE))
setkey(annotations, header)

mech_annotations <- annotations[, .SD, .SDcols=c("class", "mechanism")]
mech_annotations <- unique(mech_annotations, by=c("class", "mechanism"))
colnames(mech_annotations) <- c("Class", "Mechanism")
setkey(mech_annotations, Mechanism)

cumNorm(amr)
amr_norm <- data.table(MRcounts(amr, norm=TRUE))

amr_norm[, header :=( rownames(amr) )]
setkey(amr_norm, header)
amr_norm <- annotations[amr_norm]

amr_mech <- amr_norm[, lapply(.SD, sum), by='mechanism', .SDcols=!c('header', 'class', 'group')]
amr_mech_analytic <- newMRexperiment(counts=amr_mech[, .SD, .SDcols=!'mechanism'])
rownames(amr_mech_analytic) <- amr_mech$mechanism


metadata <- data.table(metadata[match(colnames(MRcounts(amr_mech_analytic)), metadata[, "ID"]), ])
setkey(metadata, ID)

amr_melted_mech_analytic <- melt_dt(MRcounts(amr_mech_analytic), 'Mechanism')

colnames(amr_melted_mech_analytic)[2] <- "Mechanism"
setkey(amr_melted_mech_analytic, Mechanism)

amr_melted_mech_analytic <- mech_annotations[amr_melted_mech_analytic]

amr_melted_mech_analytic[, header:=NULL]
amr_melted_mech_analytic[, group:=NULL]

setkey(amr_melted_mech_analytic, ID)

simul_data <- metadata[amr_melted_mech_analytic]
simul_data[, Group :=( paste0(Treatment, Time) )]
simul_data[, Round_count :=( round(Normalized_Count) )]
simul_data[, Treatment := NULL]
simul_data[, Time := NULL]
simul_data[, Level_ID := NULL]
setkey(simul_data, ID)

data_summary <- simul_data[,
.(
  median=median(Round_count),
  mean=mean(Round_count),
  sd=sd(Round_count),
  success=sum(Round_count > 0),
  prob=sum(Round_count == 0) / .N
), by=.(Mechanism, Group, Class)]

exit_simul_data <- simul_data[Group == "CtrlExit"]
exit_simul_data[, Normalized_Count := NULL]
exit_simul_data[, Group := NULL]
```


## Experiment 1: Sensitivity of Initial Value on Effect Size and Standard Deviation

**Experimental aim: to determine the effect of non-negative initialization value on the significance boundary of simultaneously varying effect size and standard deviation.**

### In Silico Methods

### Simulation Results


## Experiment 2: Empirical Effect Size and Standard Deviation by Univariate Feature

**Experimental aim: to determine the significance boundary as a function of simultaneously varying effect size and standard deviation for each univariate feature as seen empirically.**

### Dataset Description

Describe the dataset here including a table of the variables to be used and their summary statistics.

```{r table_data, echo=FALSE, results="asis"}
cat_table_dat <- data.table(
  Feature=c("ID", "Class", "Mechanism"),
  Description=c("Sample names",
                "Antimicrobial resistance drug class",
                "Antimicrobial resistance biological mechanism"),
  DataType=c("Categorical", "Categorical","Categorical"),
  LevelNumber=c(
    length(unique(exit_simul_data[["ID"]])),
    length(unique(exit_simul_data[["Class"]])),
    length(unique(exit_simul_data[["Mechanism"]]))
  )
)

real_table_dat <- data.table(
  SummaryStat=names(summary(exit_simul_data[["Round_count"]])),
  Value=round(as.numeric(summary(exit_simul_data[["Round_count"]])), 1)
)

knitr::kable(cat_table_dat, caption="Categorical data features.") %>% kable_styling(full_width=FALSE)

knitr::kable(real_table_dat, caption="Summary statistics for the Round_count data feature") %>% kable_styling(full_width=FALSE)
```

### In Silico Methods

### Simulation Results






